---
title: "Report - meta analysis of the correlations"
author: "Living SEB app"
output:
  bookdown::html_document2
params:
  metaRes: NA
  descriptives: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(kableExtra)
library(ggplot2)
```

## Introduction

Through the living SEB app you just conducted a three-level meta-analysis of the cross-sectional associations between the five SEB domains and the outcome of your interest.
Specific information of the meta-analysis conducted:

  - All materials, data, and analytical code are provided in the GitHub repository associated with this project.
  - All the analyses are conducted in R (R Core Team, 2022) using the ‘metafor’ package (Viechtbauer, 2010). 
  - Pearson’s r correlation coefficients were transformed to Fisher’s z scale for analysis. The results were then back-transformed to Pearson’s r
  - We employed three-level meta-analytic random-effects models using restricted maximum likelihood estimation. This approach accounts for heterogeneity both between and within studies. 
  - Confidence intervals were estimated based on a t-distribution

## Descriptive statistics

The samples included in the meta-analysis are summarized in Table \@ref(tab:descriptives)

```{r descriptives, tab.cap="Samples included and corresponding sizes"}
# The `params` object is available in the document.
descriptives <- params$descriptives

kableExtra::kable(descriptives)%>%
  kable_classic()%>%
  kable_styling(latex_options = "hold_position")


```

## Results

The results of the meta-analysis are synthesized in the following table (Table \@ref(tab:metaRes))

```{r metaRes, tab.cap="Results of the meta-analysis"}

metaRes <- params$metaRes
metaResTable <- data.frame(
      Skill = metaRes$skill,
      N = paste0(metaRes$N, " k = (", metaRes$k, ")"),
      r = format(round(metaRes$r, 3),nsmall=3),
      CI = paste0("[",format(round(metaRes$rcil,3),nsmall=3),"; ",
                  format(round(metaRes$rciu,3),nsmall=3),"]"),
      se = format(round(metaRes$se,3),nsmall=3),
      p = format(round(metaRes$p,4),3),
      q = paste0(round(metaRes$q), "(",metaRes$qdf,")",ifelse(metaRes$qp < .01, "*", "")),
      tau2 = format(round(metaRes$tau2,3),nsmall=3))

kableExtra::kable(metaResTable)%>%
  kable_classic()%>%
  kable_styling(latex_options = "hold_position")


```

Figure \@ref(fig:metaplot) shows the same results graphically. Confidence intervals are plotted together with point estimates.

```{r metaplot, fig.cap="Graphic representation of the results"}
ggplot(metaRes, aes(x = r, y = reorder(skill,5:1))) +
       geom_point(shape = 18,
                  color = "black",
                  size = 4) +
       geom_errorbar(aes(xmin = rcil, xmax = rciu), width = 0, linewidth = .8) +
       geom_vline(xintercept = c(.00), linetype = "dashed") +
       labs(x = "Meta-analytical association", y = "Skill") +
       theme_bw(base_size = 18) +
       theme(strip.text = element_text(size = 18)) +
       coord_cartesian(xlim = c(ifelse(min(metaRes$rcil) > -.05, -.15,
                                       min(metaRes$rcil)),
                                max(metaRes$rciu)))
```
