---
title: "Report - meta analysis of the correlations"
author: "Living SEB app"
output:
  bookdown::html_document2
params:
  metaRes: NA
  descriptives: NA
  outcome: NA
  outlist: NA
  dm: NA
  bibfile: NA
bibliography: '`r normalizePath(params$bibfile, winslash = "/", mustWork = TRUE)`'
nocite: "@*"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(kableExtra)
library(ggplot2)

load_xlsx_url <- function(url) {
  temp_file <- tempfile(fileext = ".xlsx")
  tryCatch({
    download.file(url, destfile = temp_file, mode = "wb")
    readxl::read_excel(temp_file)
  }, error = function(e) {
    stop("Failed to download or read Excel file: ", e$message)
  })
}

admcol_url <- "https://raw.githubusercontent.com/feracotommaso/living_SEB_review/main/data/matrix_codebook.xlsx"
admcol <- load_xlsx_url(admcol_url)

varlist <- admcol[complete.cases(admcol[,1:4]),] # List of the variables that can be used with different grain [Topic, BROAD, specific, and label]
labels_app <- setNames(varlist$label, varlist$column_name) # Create a named vector from the lookup table

#   - Labels for the plots and tables

descriptives <- params$descriptives
metaRes <- params$metaRes
metaRes$skill <- labels_app[as.character(metaRes$skill)]

out_selected <- params$outcome
out_selected <- labels_app[as.character(out_selected)]

outList <- params$outlist
dm <- params$dm

```

# Introduction

Through the living SEB app you just conducted a three-level meta-analysis of the cross-sectional associations between the five SEB domains and the outcome of your interest (`r out_selected`).
Specific information of the meta-analysis conducted:

  - All materials, data, and analytical code are provided in the GitHub repository associated with this project.
  - You can download the filtered data used for this analysis from the Shiny app.
  - All the analyses are conducted in R (R Core Team, 2022) using the ‘metafor’ package (Viechtbauer, 2010). 
  - Pearson’s r correlation coefficients were transformed to Fisher’s z scale for analysis. The results were then back-transformed to Pearson’s r
  - We employed three-level meta-analytic random-effects models using restricted maximum likelihood estimation. This approach accounts for heterogeneity both between and within studies. 
  - Confidence intervals were estimated based on a t-distribution

## Descriptive statistics

The outcome selected for this meta-analysis is:

```{r}
print(out_selected)
```


A total of `r length(unique(dm$paper_id))` papers, `r length(unique(dm$matrix_id))` samples, and `r length(dm)` were considered for this meta-analysis.

The samples included in the meta-analysis are summarized in Table \@ref(tab:descriptives).

```{r descriptives}
knitr::kable(
  descriptives,
  caption = 'Samples included and corresponding sizes',
  align = c("lllccc")
)
```

# Results

The results of the meta-analysis are synthesized in the following table (Table \@ref(tab:metaRes)).
`r metaRes$skill[which.max(metaRes$r)]` showed the strongest (`r round(metaRes$r[which.max(metaRes$r)],2)`) association with `r out_selected`, while `r metaRes$skill[which.min(metaRes$r)]` showed the lowest (`r round(metaRes$r[which.min(metaRes$r)],2)`). `r sum(metaRes$p < 0.05)` associations were significant with *p* < 0.05, `r sum(metaRes$p < 0.01)` with *p* < 0.01, and `r sum(metaRes$p < 0.001)` with *p* < 0.001.

```{r metaRes}
metaResTable <- data.frame(
      Skill = metaRes$skill,
      N = paste0(metaRes$N, " k = (", metaRes$k, ")"),
      r = format(round(metaRes$r, 3),nsmall=3),
      CI = paste0("[",format(round(metaRes$rcil,3),nsmall=3),"; ",
                  format(round(metaRes$rciu,3),nsmall=3),"]"),
      se = format(round(metaRes$se,3),nsmall=3),
      p = format(round(metaRes$p,4),3),
      q = paste0(round(metaRes$q), "(",metaRes$qdf,")",ifelse(metaRes$qp < .01, "*", "")),
      tau2 = format(round(metaRes$tau2,3),nsmall=3))

# metaResTable$Skill <- labels_app[as.character(metaResTable$Skill)]

knitr::kable(
  metaResTable,
  caption = 'Results of the meta-analysis',
  align = c("lccccccc")
)
```

Figure \@ref(fig:metaplot) shows the same results graphically. Confidence intervals are plotted together with point estimates.

```{r metaplot, fig.cap="Graphic representation of the results"}
ggplot(metaRes, aes(x = r, y = reorder(skill,5:1))) +
       geom_point(shape = 18,
                  color = "black",
                  size = 4) +
       geom_errorbar(aes(xmin = rcil, xmax = rciu), width = 0, linewidth = .8) +
       geom_vline(xintercept = c(.00), linetype = "dashed") +
       labs(x = "Meta-analytical association", y = "Skill") +
       theme_bw(base_size = 18) +
       theme(strip.text = element_text(size = 18)) +
       coord_cartesian(xlim = c(ifelse(min(metaRes$rcil) > -.05, -.15,
                                       min(metaRes$rcil)),
                                max(metaRes$rciu)))
```

## Forest plots

Forest plots for each individual SEB skill are provided below to inspect heterogeneity in the associations across samples.

```{r}
for (i in 1:length(outList)) {
  this_var <- names(outList[i])
  this_var <- labels_app[as.character(this_var)]
  row_labels <- paste0(outList[[i]]$data$author_et_al, " ",
                       outList[[i]]$data$year)
  forest(outList[[i]],
         slab = row_labels,
         atransf = transf.ztor,
         pch = 19,
         xlab = "Fisher-transformed correlation (r)",
         main = paste("Outcome:", this_var)
  )
}
```


# References